Learning Causally-Generated Stationary Time Series

### 2017-02-24 doc/paper.tex
Various updates

\Cref{mod:cgpcm2} reveals the CGCPM as a Gaussian process in which the kernel, or equivalently the power spectral density (PSD), is modelled nonparametrically. \Cref{fig:interpolation} illustrates the generative process of the CGPCM: First, a filter $h$ is generated. Then, the kernel $k_{f\cond h}$ is constructed. Finally, a sample $f\cond h$ is drawn from $\mathcal{GP}(0,k_{f \cond h}(t-t'))$. \Cref{fig:prior} visualises the corresponding prior over kernels, and \cref{fig:prior_psd} visualises the corresponding prior over PSDs. Note that in \cref{fig:prior_psd} the prior for the GPCM has a low-pass structure, whereas that for the CGPCM decays more slowly.

@@

\begin{figure}[t]
    \centering
    \begin{tabularx}{\linewidth}{>{\centering}X>{\centering}X}
        GPCM & CGPCM
    \end{tabularx}
    \includegraphics[width=\linewidth, height=3cm]{resources/cropped/prior_psd.pdf}
    \caption{Prior distribution over PSDs in the GPCM and CGPCM. Lines correspond to means and gradients correspond to uncertainty.}
    \label{fig:prior_psd}
\end{figure}

@@

\subsection{Speech Modelling}
Coming up.

>>>>

\Cref{mod:cgpcm2} reveals the CGCPM as a Gaussian process in which the kernel, or equivalently the power spectral density (PSD), is modelled nonparametrically. \Cref{fig:interpolation} illustrates the generative process of the CGPCM: First, a filter $h$ is generated. Then, the kernel $k_{f\cond h}$ is constructed. Finally, a sample $f\cond h$ is drawn from $\mathcal{GP}(0,k_{f \cond h}(t-t'))$. \Cref{fig:prior} visualises the corresponding prior over kernels, and \cref{fig:prior_psd} visualises the corresponding prior over PSDs. Note that the prior over PSDs for the GPCM has a confident low-pass structure, whereas that for the CGPCM has support for more slowly decaying spectra.

@@

\begin{figure}[t]
    \centering
    \begin{tabularx}{\linewidth}{>{\centering}X>{\centering}X}
        ~~GPCM & ~~~~~~CGPCM
    \end{tabularx}
    \includegraphics[width=\linewidth, height=3cm]{resources/cropped/prior_psd.pdf}
    \caption{Prior distribution over PSDs in the GPCM and CGPCM. The unit on the $y$ axis is decibel. Lines correspond to means and gradients correspond to uncertainty.}
    \label{fig:prior_psd}
\end{figure}

@@

\subsection{Speech}
Coming up.
